Results discussion

### 2024-11-14 pages/results_discussion.qmd
docs(general): minor bits / tidying / removing resolved TODO
chore(general): minor changes

::: {.callout-note}

## What is on this page?

* Reflections from the reproduction and evaluation, broadly grouped into two categories
* Headline findings
* Relationship between reproduction and evaluation
* Some other things I want to mention

@@

>>>>

@@

Importance of the timings. It often took alot of time to get something working. That is likely not feasible in practice. Andy anecdotally commented on the max amount of time that someone in the NHS would likely spend on something troubleshooting before moving on.
